Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-21 WSSSPE2_report/WSSSPE2_review.tex
edits to lightning talks

\item \textbf{Abani Patra: Execute it.}
%Univ at Buffalo, SUNY
The primary purpose of this presentation was to reinforce the value of
an available and easily accessible platform for executing scientific software,
e.g., HUBzero, to access XSEDE or other computing resources.
Such a platform for executing benchmark problems (even at small
scale) allows the developer community access to a reference implementation and
provides an easy way to train the larger user community. A second focus of this
presentation was the idea that much more attention needs to be paid to the
integrated use of simulation tools inside complex workflows. True usability
needs supporting the user community workflow. \todo{revise}

@@

% \item Jakob Blomer: The Need for a Versioned Data Analysis Environment

>>>>

\item \textbf{Abani Patra: Execute it.}
%Univ at Buffalo, SUNY
Patra discussed the value of
an available and easily accessible platform for executing scientific software,
e.g., HUBzero, to access XSEDE or other computing resources.
Such a platform for executing benchmark problems (even at small
scale) allows the developer community access to a reference implementation and
provides an easy way to train the larger user community. A second focus of this
presentation was the idea that much more attention needs to be paid to the
integrated use of simulation tools inside complex workflows. True usability
needs supporting the user community workflow. \todo{revise}

@@

\item \textbf{Jakob Blomer: The Need for a Versioned Data Analysis Environment}
%
Large-scale scientific endeavors, such as the discovery of the Higgs
boson at the Large Hadron Collider (LHC), often rely on complex software
stacks.  Maintaining thousands of dependencies of software
libraries and operating system versions has shown that despite
source code availability, the setup and the validation of a minimal
usable analysis environment can easily become prohibitively expensive.
%There is a substantial gap between merely having access to open source
%software and the ability to create a data analysis runtime environment.
 In high-energy physics, a
special purpose, open-source, versioning and snapshotting file system
(CernVM-FS) that is used to capture and distribute entire software stacks,
providing instant access to ready-to-run data analysis environments,
proved to be very useful.
% for the global scientific community as well as for
%interested citizens, for instance through the CERN Open Data Portal
%(http://opendata.cern.ch). \todo{revise}
